\begin{thebibliography}{99}

\bibitem{LittleRubin2019}
R.~J.~A. Little and D.~B. Rubin, \emph{Statistical Analysis with Missing Data}, 3rd~ed. Wiley, 2019.

\bibitem{Cleveland1990STL}
R.~B. Cleveland, W.~S. Cleveland, J.~E. McRae, and I. Terpenning, "STL: A seasonal-trend decomposition procedure based on LOESS," \emph{Journal of Official Statistics}, vol.~6, no.~1, pp.~3--73, 1990.

\bibitem{HyndmanAthanasopoulosFPP3}
R.~J. Hyndman and G. Athanasopoulos, \emph{Forecasting: Principles and Practice}, 3rd~ed. OTexts, 2021.

\bibitem{Moritz2015ImputeTS}
S. Moritz, A. Sard'a, T. Bartz-Beielstein, M. Zaefferer, and J. Stork, "Comparison of different methods for univariate time series imputation in R," \emph{arXiv:1510.03924}, 2015.

\bibitem{Zhang2018IEEEAccess}
S. Zhang, J. Zhang, and Y. Qin, "A decomposition-based missing value imputation method for time series," \emph{IEEE Access}, vol.~6, pp.~5934--5945, 2018.

\bibitem{ZhangLiu2020Sensors}
Y. Zhang and Y. Liu, "Time series imputation based on seasonal decomposition and regression," \emph{Sensors}, vol.~20, no.~13, p.~3679, 2020.

\bibitem{CheemaLin2011}
M.~A. Cheema and X. Lin, "Interpolation methods for spatio-temporal data," \emph{Knowledge and Information Systems}, vol.~27, no.~3, pp.~303--334, 2011.

\bibitem{Kalman1960}
R.~E. Kalman, "A new approach to linear filtering and prediction problems," \emph{ASME Journal of Basic Engineering}, vol.~82, no.~1, pp.~35--45, 1960.

\bibitem{Harvey1989}
A.~C. Harvey, \emph{Forecasting, Structural Time Series Models and the Kalman Filter}. Cambridge University Press, 1989.

\bibitem{DurbinKoopman2012}
J. Durbin and S.~J. Koopman, \emph{Time Series Analysis by State Space Methods}, 2nd~ed. Oxford University Press, 2012.

\bibitem{ShumwayStoffer1982}
R.~H. Shumway and D.~S. Stoffer, "An approach to time series smoothing and forecasting using the EM algorithm," \emph{Journal of Time Series Analysis}, vol.~3, no.~4, pp.~253--264, 1982.

\bibitem{DeLivera2011TBATS}
A.~M. De~Livera, R.~J. Hyndman, and R.~D. Snyder, "Forecasting time series with complex seasonal patterns using exponential smoothing," \emph{Journal of the American Statistical Association}, vol.~106, no.~496, pp.~1513--1527, 2011.

\bibitem{HarveyKoopman1993}
A.~C. Harvey and S.~J. Koopman, "Forecasting hourly electricity demand using time-varying splines," \emph{Journal of the American Statistical Association}, vol.~88, pp.~1228--1236, 1993.

\bibitem{HyndmanKoehler2006}
R.~J. Hyndman and A.~B. Koehler, "Another look at measures of forecast accuracy," \emph{International Journal of Forecasting}, vol.~22, no.~4, pp.~679--688, 2006.

\bibitem{Arias2021Survey}
M. Arias et al., "A survey of time series imputation methods," \emph{ACM Computing Surveys}, vol.~54, no.~8, Article~160, 2021.

\bibitem{Chen2016EnergyBuildings}
Y. Chen, Y. Lv, F.-Y. Wang, X. Li, and Y. Wang, "Detecting and imputing anomalies in building energy consumption data," \emph{Energy and Buildings}, vol.~127, pp.~181--195, 2016.

\bibitem{Fan2014EnergyBuildings}
C. Fan, F. Xiao, and S. Wang, "Development of prediction models for next-day building energy consumption," \emph{Energy and Buildings}, vol.~76, pp.~73--84, 2014.

\bibitem{HongPinsonFan2014GEFCom2012}
T. Hong, P. Pinson, and S. Fan, "Global energy forecasting competition 2012," \emph{International Journal of Forecasting}, vol.~30, no.~2, pp.~357--363, 2014.

\bibitem{Cao2018BRITS}
W. Cao, D. Wang, J. Li, H. Zhou, L. Li, and Y. Li, "BRITS: Bidirectional recurrent imputation for time series," in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2018.

\bibitem{Che2016GRUD}
Z. Che, S. Purushotham, K. Cho, D. Sontag, and Y. Liu, "Recurrent neural networks for multivariate time series with missing values (GRU-D)," \emph{arXiv:1606.01865}, 2016.

\bibitem{Du2022SAITS}
W. Du, D. C^ot'e, and Y. Liu, "SAITS: Self-attention-based imputation for time series," \emph{arXiv:2202.08516}, 2022.

\bibitem{Tashiro2021CSDI}
Y. Tashiro, J. Song, Y. Song, and S. Ermon, "CSDI: Conditional score-based diffusion models for probabilistic time series imputation," in \emph{NeurIPS}, 2021.

\bibitem{Zhao2020WNNKalman}
F. Zhao, L. Wang, J. Chen, M. Zhang, W. Xu, J. Li, and C. Zhao, ``Multi-feature weighted nearest neighbor data association and tracking algorithm based on Kalman filter,'' \emph{Journal of Hebei University of Science and Technology}, vol. 41, no. 3, pp. 218--224, Jun. 2020, doi: 10.7535/hbkd.2020yx03003.

\bibitem{Asahiro2010WNNGraphCycles}
Y. Asahiro, E. Miyano, S. Miyazaki, and T. Yoshimuta, ``Weighted nearest neighbor algorithms for the graph exploration problem on cycles,'' \emph{Information Processing Letters}, vol. 110, no. 3, pp. 93--98, Jan. 2010, doi: 10.1016/j.ipl.2009.10.013.

\bibitem{CostSalzberg1993WNN}
S. Cost and S. Salzberg, ``A weighted nearest neighbor algorithm for learning with symbolic features,'' \emph{Machine Learning}, vol. 10, no. 1, pp. 57--78, 1993, doi: 10.1023/A:1022664626993.

\bibitem{Samworth2012OptimalWNN}
R. J. Samworth, ``Optimal weighted nearest neighbour classifiers,'' \emph{The Annals of Statistics}, vol. 40, no. 5, pp. 2733--2763, Oct. 2012, doi: 10.1214/12-AOS1049.

\bibitem{Wang2014MTSSimilarity}
J. Wang, Y. Zhu, S. Li, D. Wan, and P. Zhang, ``Multivariate Time Series Similarity Searching,'' \emph{ScientificWorldJournal}, vol. 2014, Article ID 851017, May 2014, doi: 10.1155/2014/851017.

\bibitem{Tajmouati2021ConformalNNTS}
S. Tajmouati, B. El Wahbi, and M. Dakkoun, ``Applying Regression Conformal Prediction with Nearest Neighbors to time series data,'' arXiv:2110.13031, Oct. 2021, doi: 10.48550/arXiv.2110.13031.

\bibitem{Carlson1998WNNDataMiningReport}
R. R. Carlson, P. F. Chavez, and K. L. Boyack, ``Final Report: Weighted Neighbor Data Mining,'' Sandia National Laboratories, Tech. Rep. SAND98-0605, Mar. 1998, doi: 10.2172/773910.

\bibitem{Oron2018BestBuddies}
S. Oron, T. Dekel, T. Xue, W. T. Freeman, and S. Avidan, ``Best-Buddies Similarity---Robust Template Matching Using Mutual Nearest Neighbors,'' \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 40, no. 8, pp. 1799--1813, Aug. 2018, doi: 10.1109/TPAMI.2017.2737424.


\end{thebibliography}